\documentclass[a4paper,11pt]{ltjsarticle}
\input{../files/preamble}

\begin{document}
\section{パッキングレングスとは？}

\subsection{当初の定義}

パッキングレングスは、以下のように定義される\footnote{
    Witten, T.A.; Milner, S.T.; Wang, Z.-G. in Multiphase Macromolecular Systems; Culbertson, B.M., Ed.; Plenum: New York, 1989.
}。
\begin{equation}
    p=\dfrac{M}{\langle R^2 \rangle_0 \rho N_a}
    \label{def_PL}
\end{equation}
ここで、$M$はポリマー鎖の分子量、$\langle R^2 \rangle_0$はシータ状態での平均自乗末端間距離、$\rho$は密度、$N_a$はアボガドロ数である。
なお、この定義の意味は一本のポリマー鎖が占有する体積$\dfrac{M}{\rho N_a}$を$\langle R^2 \rangle_0$で除したものとされているが、物理的な直感に結びつけるのは困難である。

\subsection{Fettersらのアプローチ}
この$p$というパラメタの意味について考えてみよう。

式\eqref{def_PL}は、Floryの特性比$C_{\infty}$\footnote{
特性費の定義は、$C_{\infty}=\dfrac{\langle R^2 \rangle_0}{n b^2}$であり、ここでの$n, b$はモノマーユニットの数とその長さ（経路長を$n$で割ったもの）を表す。
}により、

\begin{align}
    p&=\dfrac{M}{\langle R^2 \rangle_0 \rho N_a} \\
    &=\dfrac{M}{C_{\infty} n b^2 \rho N_a} \\
    &=\dfrac{m_b}{C_{\infty}b^2\rho N_a}
\end{align}

ここで、ポリマー鎖を形成するモノマー1個の体積$V_b$を以下のように見積もると、
\begin{equation}
    V_b=\dfrac{n}{\rho N_a}
\end{equation}

% Equation (1A) can also be expressed in terms of Flory’s characteristic ratio as 

% The average volume of a chain per bond is given as 

% Thus, the packing length can be expressed as 

% The parameter V 
% , where h represents the diameter of a cylinder of length  
% 0 
% swept out 
% by the chain repeat unit. 

% Thus, 

% where the product C 
%  
%  
% 0 
% is the Kuhn step length 
% l. One can thus think of a chain as being made up of freely jointed rods of length l = C and diameter h. The packing length is thus proportional to the ratio of the cross-sectional area to the length of each rod. Hence, the smaller h is with respect to the skinnier the chain and the smaller p and Vb 

ポリマー鎖中の繰り返しユニットの直径に対応すると考えられる。

\end{document}

